DNSKEY Management

### 2012-12-04 paper/paper.tex

In this paper we will first remind of the principal necessary
operations for key management in DNSSEC. Then we will give the reader
an overview of the current status of DNSSEC deployment in the Internet
to put the in-detail discussion about key management into the right
context.

@@

@@

\subsubsection{Single administrative domain}
Basically, once an organization has its main domain signed, it is relatively easy for any sub-entity within said organization to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant for such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are.
\subsection{Disabling DNSSEC}

>>>>

In this paper we will first remind of the concepts and operations in
DNSSEC relevant for key management. Then we will give the reader an
overview of the current status of DNSSEC deployment in the Internet to
put the in-detail discussion about key management into the right
context.

@@

\subsection{Chain of Trust}
%% TODO add

@@

\subsubsection{Single administrative domain}
Basically, once an organization has its main domain signed, it is relatively easy for any sub-entity within said organization to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
\subsection{Disabling DNSSEC}
